Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-08-25 paper/uist_2016/paper.tex
audacious changes of the system section; to be continued..

Capturing a memory is a fundamental part of human nature. Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day. Then came the cameras, to take with us when we expected a memorable moment. Now smartphone cameras are always nearby, ready for an opportunity to capture both the spectacular and the mundane. This paper introduces Rewind, the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.

@@

\section{The Rewind System}
Rewind is a system that takes user geolocation tracking data as input and outputs systematically selected location points that are shown to the user as a photo-video pair: a Google Street View image of the location and a Rewind that includes the location. A user's geolocation tracking data includes latitude and longitude coordinates, timestamps of when the user was at given coordinates, and an accuracy score for each geolocation record. Rewind expects the geolocation data to be formatted as JSON (but is compatible with other location-based formats like GPX), particularly in the same format that Google Takeout generates for Location History.

Rewind is implemented as a client-side only application and therefore does not transfer sensitive user data or store it; it does not have a server component for communication. The system is written with standard web technologies: HTML5, CSS, and JavaScript, in addition to various open source libraries and services. These libraries include the Google Maps API, determining routes between location points and retrieving Google Street View images of any given location; the StreetviewSequence.js library is also used in the process of generating Rewinds \cite{streetviewsequence}. The library takes in data in the form of a Google Route and composes a video sequence by stitching together Google Street View images from multiple points on the given route (Figure~\ref{fig:rewinds}). The CamanJS library \cite{caman} is used to manipulate the appearance of Google Street View images such as brightness, contrast, and saturation in order to better replicate the environmental conditions at a given time. More sophisticated image manipulation techniques were investigated \cite{laffont2014transient} but deemed to slow for Rewind's current real-time use.

Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user. First, the user uploads their geolocation data to Rewind's main page. From there, less accurate location records are filtered out using the accuracy ratings provided by Google. Any location recording that has an accuracy radius greater than 200 meters is ignored. The accepted data is stored in memory to prepare the user's location points. A location frequency map is generated by counting the number of times each location appears in history. In order to minimize the minor coordinate variations and to identify close coordinate pair records, only the first 3 decimal digits of coordinates are used when counting the number of appearances. The location with the highest number of visits is marked as user's home. We then use the Haversine formula to calculate the individual distance between all given locations and the user's home, attaching the distance data to the location. % Finally, for the user study, Rewind generates the user's set of locations based on visit frequency: 5 from the least visited locations, 3 from the most visited locations, and 2 randomly selected locations.

Once the location set is determined, photos are retrieved from Google Street View and manipulated for time of year and time of day. For each selected location, a Google Street View image is requested and the timestamp of when the user visited the location is used to determine how the image should be manipulated to appear as close as possible to what the user saw. For the time of year, adjustments are made to the image's saturation (Figure~\ref{fig:season}), and for the time of day (Figure~\ref{fig:timeofday}), adjustments are made to the image's brightness. For example, if the location's timestamp denotes the summer, the image will be adjusted to have higher saturation to account for the vivid colors during that season. In the same vein, an image taken at noon will be adjusted to have higher brightness whereas an image taken at a time closer to sunset will be adjusted for lower brightness to account for the amount of sunlight captured. Taking this into account, Rewind evaluates the saturation and brightness of each Google Street View image as it is retrieved, and makes adjustments to mimic the actual date and time of user's visit. Weather adjustments for images are made at the same time as date and time adjustments. Using data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations, Rewind checks for factors that would require image adjustments. In our study, we adjusted only images from [anonymized: our state/province] and only for precipitation. However, it would not be difficult to do this for images from any location with a larger weather database, and other types of weather can be used to make adjustments besides precipitation. For our study, if there was precipitation at the time the user visited the location, the contrast is lowered to imitate cloudiness or rain. After these adjustments, the location set is now ready to be shown to the user.

@@

\subsubsection{Travel Companions}
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.

>>>>

Preserving memorable moments is a fundamental part of human nature. Not long ago, we chronicled significant moments in our lives through journals and diaries, to be filled at the end of the day. Then came the cameras, to take with us when we expected a memorable moment. Now smartphone cameras are always nearby, ready for an opportunity to capture both the spectacular and the mundane. This paper introduces Rewind, the next evolution in digital memories: nothing to prepare or take out, just rewind and replay a trip from the past.

@@

\section{The Rewind System}
\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by ***(Neel Joshi's and Johannes Kopf's work from Microsoft)****, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimentional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party Javascript libraries, and therefore does not transfer sensitive user data nor store it.

\subsubsection{Route Determination} (needs to be rephrased? perhaps?)
A user's geolocation tracking data includes latitude and longitude coordinates, timestamps of when the user was at given coordinates, and an accuracy score for each geolocation record. \textit{Rewind} expects JSON formatted data, and is also compatible with other location-based formats such as GPX. Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user. First, the user uploads their geolocation data to Rewind's main page. From there, less accurate location records are filtered out using the accuracy ratings provided by Google. Any location recording that has an accuracy radius greater than 200 meters is ignored. The accepted data is stored in memory to prepare the user's location points. A location frequency map is generated by counting the number of times each location appears in history. In order to minimize the minor coordinate variations and to identify close coordinate pair records, only the first 3 decimal digits of coordinates are used when counting the number of appearances. The location with the highest number of visits is marked as user's home. We then use the Haversine formula to calculate the individual distance between all given locations and the user's home, attaching the distance data to the location.

\subsubsection{Hyperlapse Creation} 
The composition of one video recollection is consist of two hundred Google Street View images snapshotting the chosen route. Before stitching the imageries together using StreetviewSequence Javascript Library \cite{streetviewsequence}, we performed pixel-wise adjustment on each Google Street View image to reveal time-specific cues including diurnal cycle, seasonal characteristics and meteorological attributes. To achieve this, we used naive HVS and RGB color space mapping for sky and plantation approximation and modification. Similar to the method described by ****Irfanullah (An efficient approach for sky detection)*****, we generalized color mapping streamlines to estimate sky, cloud and plantation. (need to expand on this and mention Caman) For meteorological conditions in particular, we prepared a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations for weather lookup. (need to expand too)
-- to be continued

@@

\subsubsection{Travel Companions}
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% fare of trips in which the participant is traveling with others. The data shows clearly that a Rewind is considered much more valuable if the trip it depicts was taken with company.
